---
title:  "AddGene web-scraping validation"
author: "Sam Hunter"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = '/bio/CoreWork/2019.11.18-Trimmer-Hybridoma-Seq/2020-02-07-run-rerun_of_27-samples-SMARTPCR')
library(kableExtra)
library(ggplot2)
library(stringr)
library(msaR)
library(DECIPHER)
options(stringsAsFactors=F)

```


```{r readdata, echo=FALSE, results="hide"}
# A quick little test to make sure that everything I pulled from Addgene matches the samples that
# that were in the old file from the Trimmer lab.

# Read in original sequences (from Trimmer file)
orig = read.table("./backup/03-AnnotatedResults/Sanger_samples_Sequences.tsv", header=T, as.is=T, sep='\t')
orig$ASV = gsub(' ', '', orig$ASV)  # get rid of any spaces

new = read.table('03-AnnotatedResults/Sanger_samples_Sequences.tsv', header=T, as.is=T, sep='\t')
new$ASV = gsub(' ', '', new$ASV)  # get rid of any spaces

okey = paste(orig$Sample_Name, orig$Chain, sep='.')
rownames(orig) = okey

nkey = paste(new$Sample_Name, new$Chain, sep='.')
rownames(new) = nkey
```


----------


### First, are all of the old keys in the new dataset?

#### List samples missing from the old dataset:

```{r compare_OldVSNew, echo=FALSE}

kable(orig[!(okey %in% nkey), c("Sample_Name", "plate", "MabID", "Chain")]) %>%
  kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = 0)
```



TODO: the Gs samples need to be added


Something strang is going on with Psanger_128631 (L28/4R) in the old dataset. Addgene ID 149453 has this MabID on web site.
It looks like 128631 also exists on the web page, but can't be searched for.

#### ---> Addgene ID 128631 and 149453 have identical sequences

```{r compareLC}
orig$ASV[orig$Sample_Name == 'Psanger_128631' & orig$Chain=='LC'] == 
new$ASV[new$Sample_Name == 'Psanger_149453' & new$Chain=='LC']
```

```{r compareHC}
orig$ASV[orig$Sample_Name == 'Psanger_128631' & orig$Chain=='HC'] == 
new$ASV[new$Sample_Name == 'Psanger_149453' & new$Chain=='HC']
```

\
\


----------

\
\

### Second, are all of the AddGene sequences also in the orignal dataset?

List samples missing from the old dataset that are present on AddGene:
```{r compare_NewVSOld}
kable(new[!(nkey %in% okey), c("Sample_Name", "plate", "MabID", "Chain")]) %>%
  kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = 0)

```

There are 22 new samples, this is expected because Belvin has sent 13 + 8 new samples in email, 
and there is the 149453 sample that isn't accounted for.

----------


#### Third, check that sequences are identical for all matching samples:
```{r compareSequences}
commonk = intersect(nkey, okey)
table(orig$ASV[match(commonk, okey)] == new$ASV[match(commonk, nkey)])
```
Unfortunately it looks like 7 sequences are not identical.

Extract sequences that don't match, write to table:
```{r makeMismatchTable, echo=FALSE}

mismatch = commonk[!(orig$ASV[match(commonk, okey)] == new$ASV[match(commonk, nkey)])]

mismatches = rbind(data.frame(Source='original', orig[mismatch,]), 
                   data.frame(Source='addgene', new[mismatch,]))

mismatches = mismatches[order(mismatches$Sample_Name, mismatches$Chain), ]

kable(mismatches[, c("Source", "Sample_Name", "plate", "MabID", "Chain")]) %>%
  kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = 0)

write.table(mismatches, file='addgene_spreadsheet_discrepancies.tsv', row.names=F, sep='\t')
```


### Create alingments for each pair this isn't identical:


\
\

#### `r paste(mismatches$Sample_Name[1], mismatches$MabID[1], mismatches$Chain[1], sep='.')`

\

```{r plotalignment1.2, echo=FALSE}
x = c(1,2)
dna = DNAStringSet(mismatches$ASV[x])
names(dna) = paste(mismatches$Sample_Name, mismatches$Source, sep='.')[x]
alignedDNA = AlignSeqs(dna, verbose=F)
msaR(alignedDNA, menu=F, height=100, overviewbox = F, conservation=T, labelNameLength=175)

```

\
\
\
\

#### `r paste(mismatches$Sample_Name[3], mismatches$MabID[3], mismatches$Chain[3], sep='.')`

\

```{r plotalignment3.4, echo=FALSE}
x = c(3,4)
dna = DNAStringSet(mismatches$ASV[x])
names(dna) = paste(mismatches$Sample_Name, mismatches$Source, sep='.')[x]
alignedDNA = AlignSeqs(dna, verbose=F)
msaR(alignedDNA, menu=F, height=100, overviewbox = F, conservation=T, labelNameLength=175)

```

\
\
\
\

#### `r paste(mismatches$Sample_Name[5], mismatches$MabID[5], mismatches$Chain[5], sep='.')`

\

```{r plotalignment5.6, echo=FALSE}
x = c(5,6)
dna = DNAStringSet(mismatches$ASV[x])
names(dna) = paste(mismatches$Sample_Name, mismatches$Source, sep='.')[x]
alignedDNA = AlignSeqs(dna, verbose=F)
msaR(alignedDNA, menu=F, height=100, overviewbox = F, conservation=T, labelNameLength=175)

```

\
\
\
\

#### `r paste(mismatches$Sample_Name[7], mismatches$MabID[7], mismatches$Chain[7], sep='.')`

\

```{r plotalignment7.8, echo=FALSE}
x = c(7,8)
dna = DNAStringSet(mismatches$ASV[x])
names(dna) = paste(mismatches$Sample_Name, mismatches$Source, sep='.')[x]
alignedDNA = AlignSeqs(dna, verbose=F)
msaR(alignedDNA, menu=F, height=100, overviewbox = F, conservation=T, labelNameLength=175)

```

\
\
\
\

#### `r paste(mismatches$Sample_Name[9], mismatches$MabID[9], mismatches$Chain[9], sep='.')`

\

```{r plotalignment9.10, echo=FALSE}
x = c(9,10)
dna = DNAStringSet(mismatches$ASV[x])
names(dna) = paste(mismatches$Sample_Name, mismatches$Source, sep='.')[x]
alignedDNA = AlignSeqs(dna, verbose=F)
msaR(alignedDNA, menu=F, height=100, overviewbox = F, conservation=T, labelNameLength=175)

```

\
\
\
\

#### `r paste(mismatches$Sample_Name[11], mismatches$MabID[11], mismatches$Chain[11], sep='.')`

\

```{r plotalignment11.12, echo=FALSE}
x = c(11,12)
dna = DNAStringSet(mismatches$ASV[x])
names(dna) = paste(mismatches$Sample_Name, mismatches$Source, sep='.')[x]
alignedDNA = AlignSeqs(dna, verbose=F)
msaR(alignedDNA, menu=F, height=100, overviewbox = F, conservation=T, labelNameLength=175)

```

\
\
\
\


##### `r paste(mismatches$Sample_Name[13], mismatches$MabID[13], mismatches$Chain[13], sep='.')`

\

```{r plotalignment13.14, echo=FALSE}
x = c(13,14)
dna = DNAStringSet(mismatches$ASV[x])
names(dna) = paste(mismatches$Sample_Name, mismatches$Source, sep='.')[x]
alignedDNA = AlignSeqs(dna, verbose=F)
msaR(alignedDNA, menu=F, height=100, overviewbox = F, conservation=T, labelNameLength=175)
# Rscript -e "rmarkdown::render('compare_AddGeneSeqs.RMD')"

```

\
\
\


#### AA predictions:
```{css}
.main-container {
    max-width: 100%;
}
```
```{r compare_AA, echo=FALSE}
df = mismatches[,c("Sample_Name", "Source", "MabID", "Chain", "AA")]
df$AA = gsub("`", "|", df$AA)
kable(df) %>%
  kable_styling("striped", full_width = T) %>%
  row_spec(0, angle = 0)
```

